---
title: "Main analysis | POINT | Nonverbal action interpretation guides novel word disambiguation in 12-month-olds"
author: /
output:
  html_document:
    toc: yes
    toc_float: yes
---

# Data structure

data_differencescores.xlsx contains:

* $Experiment$       -- Experiment 1, Experiment 2, Experiment 3, Experiment 4 
* $ID$               -- unique ID identifying each participant
* $Condition$         -- word heard at test (trained v. novel)
* $dfbin1$     --  difference scores in time bin 1
* $dfbin2$     --  difference scores in time bin 2
* $dfbin3$     --  difference scores in time bin 3
* $dfbin4$     --  difference scores in time bin 4
* $dfbin5$     --  difference scores in time bin 4
* $dftrial$
* $proptrial$

# Libraries and set up
```{r message=FALSE, warning=FALSE, , paged.print=FALSE}
library(tidyverse)
library(readxl)
library(rstatix)
library(ggpubr)
library(emmeans)
library(afex)
library(sjstats)
library(lsr)
library(sjPlot) # making tables
library(kableExtra) # making tables
library(broom)
library(broom.mixed)
library(thinkr)
```

# Load data

Load the data.

```{r }
#Difference scores
df <- read_excel("data/datadftest.xlsx",
                      sheet="data", na = "NaN")
```

Prepare the dataset.
```{r }
#Convert Condtition, Id, Experiment, Trial as factor
df$Condition <- factor(df$Condition, levels = c("Trained","Novel"))
df$Subject <- factor(df$Subject)
df$Experiment <- factor(df$Experiment,
                             levels = c(1,2,3,4),
                             labels = c("Experiment 1", "Experiment 2",
                                        "Experiment 3", "Experiment 4"))

dflong <- df %>% 
  gather(key="Time", value="DiffScore", c("dfbin1","dfbin2","dfbin3", "dfbin4","dfbin5")) %>%
  mutate(Time = factor(Time, ordered = TRUE,
                      levels = c("dfbin1","dfbin2","dfbin3", "dfbin4", "dfbin5"),
                      labels = c("0-1 s", "1-2 s", "2-3 s", "3-4 s", "4-5 s")))

#Check the data structure
str(dflong)
```

```{r}
e1data <- subset(dflong, Experiment == "Experiment 1") 
e2data <- subset(dflong, Experiment == "Experiment 2") 
e3data <- subset(dflong, Experiment == "Experiment 3")
e4data <- subset(dflong, Experiment == "Experiment 4")
```


# Experiment 1 (Point + Name)

```{r }
head(e1data)
```
### Descriptive statistics
Compute the summary descriptive statistics.
```{r echo=FALSE}
e1data %>%
  group_by(Condition, Time) %>%
  get_summary_stats(DiffScore,type = "mean_sd")
```

### Normality

Perform the Shapiro-Wilk test of normality.

```{r echo=FALSE}
#Normality
e1data %>%
  group_by(Condition, Time) %>%
  shapiro_test(DiffScore)
```

Draw the histograms of the data.

```{r echo=FALSE, warning=FALSE}
p <- gghistogram(e1data, x = "DiffScore",
                 ggtheme = theme_pubclean(),
                 add = "mean", rug = TRUE, bins = "8",
                 color = "Condition", fill = "Condition", alpha = .2,
                 palette = c("#00AFBB", "#E7B800"),
                 xlab = "Difference Score") +
          facet_grid(Condition ~ Time, labeller = "label_both")

p + 
  font("x.text", size = 6.5) 
```


Draws the correlation between the data and the normal distribution.

```{r echo=FALSE, warning=FALSE}
ggqqplot(e1data, "DiffScore", ggtheme = theme_pubclean()) +
          facet_grid(Condition ~ Time, labeller = "label_both")
```

### GLMM (resubmission)

```{r}
me1.fit1 <- lmer(DiffScore ~ Condition + (1|Subject), data = e1data, REML = FALSE)
me1.fit2 <- lmer(DiffScore ~ Condition+Time + (1|Subject), data = e1data, REML = FALSE)
me1.fit3 <- lmer(DiffScore ~ Condition*Time + (1|Subject), data = e1data, REML = FALSE)
anova(me1.fit1,me1.fit2)
anova(me1.fit2,me1.fit3)
```

```{r}
summary(me1.fit3)
shapiro.test(residuals(me1.fit3))
confint(me1.fit3)
```

Make a summary table 
```{r}
anova(me1.fit3)
```

```{r}
tab_model(me1.fit3)
```

### ANOVA (submission)

A repeated-measures ANOVA with:
* $condition$ as a within-subject factor
* $test bin$ (0-1 sec v. 1-2 sec v. 2-3 sec v. 3-4 sec) as a within-subject factor

```{r echo=FALSE, warning=FALSE}
#Run the analysis
aux <- e1data %>% 
  filter(Time != "bin5")
ae1 <- aov_car(DiffScore ~ Time*Condition + Error(Subject/Time*Condition), 
                   data = aux, type = 3)
#Display the results
summary(ae1)
eta_sq(ae1, partial = TRUE)
cohens_f(ae1, partial = TRUE)
```

### Figures

```{r }
e1plot <- e1data 

e1plot$Time <- factor(e1plot$Time, 
                      levels = c("0-1 s", "1-2 s", "2-3 s", "3-4 s", "4-5 s"))

e1s <- e1plot %>%
  group_by(Condition, Time) %>%
  get_summary_stats(DiffScore,type = "mean_se")
  
e1s$Time <- factor(e1s$Time)
```

```{r }
library(ggrepel)
library(grid)
grob <- grobTree(textGrob("Object targeted by the action", x=.6,  y=.9, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
grob2 <- grobTree(textGrob("Distractor", x=.86,  y=.1, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
```
 
#### Line plots

```{r echo=FALSE}
pe1.l <- ggplot(data = e1s,aes(x=Time, y = mean, color=Condition,group=Condition)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20),
                plot.subtitle = element_text(size = 16, face = "italic")) +
  geom_point(size=3) +
  geom_line(aes(linetype=Condition),size=1) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  scale_fill_manual(values = c("steelblue", "orange")) +
  scale_color_manual(values = c("steelblue", "orange")) +
  scale_y_continuous(name="Difference Score", limits=c(-.8, .8)) +
  ggtitle("Experiment 1", subtitle = "Pointing + Naming") +
  annotation_custom(grob) +
  annotation_custom(grob2)

pe1.l
```

#### Box plots

```{r}
b1 <- ggplot(data = e1data, aes(x=Time, y=DiffScore)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 14)) +
  geom_boxplot(aes(fill=Condition), position = position_dodge(.9), alpha = .05) +
  geom_jitter(aes(color=Condition),position = position_jitterdodge(.15)) +
  scale_y_continuous(name="Difference Score", limits=c(-1.25, 1.25)) +
  scale_fill_manual(values = c("steelblue", "orange")) +
  scale_color_manual(values = c("steelblue", "orange")) +
  ggtitle("  \n ")

b1
```

### Follow-up tests

#### Comparisons between conditions

To solve the significant interaction between condition and time, we conducted paired-samples t tests within each time window.

```{r}
t.test(DiffScore ~ Condition, data = e1data %>% filter(Time=="0-1 s"), paired = TRUE)
cohensD(DiffScore ~ Condition, data = e1data %>% filter(Time=="0-1 s"), method = "paired")
bin1 <- lmer(DiffScore ~ Condition + (1|Subject), data = e1data %>% filter(Time=="0-1 s"), REML = FALSE)
summary(bin1)
```

During the pretest and remainder of the test, there was no significant differences in response to trained and novel words (all *ps* > .35).

```{r}
# 1-2 s
t.test(DiffScore ~ Condition, data = e1data %>% filter(Time=="1-2 s"), paired = TRUE)
bin2 <- lmer(DiffScore ~ Condition + (1|Subject), data = e1data %>% filter(Time=="1-2 s"), REML = FALSE)
summary(bin2)
# 2-3 s
t.test(DiffScore ~ Condition, data = e1data %>% filter(Time=="2-3 s"), paired = TRUE)
bin3 <- lmer(DiffScore ~ Condition + (1|Subject), data = e1data %>% filter(Time=="2-3 s"), REML = FALSE)
summary(bin3)
# 3-4 s
t.test(DiffScore ~ Condition, data = e1data %>% filter(Time=="3-4 s"), paired = TRUE)
# 4-5 s
t.test(DiffScore ~ Condition, data = e1data %>% filter(Time=="4-5 s"), paired = TRUE)
```

#### Comparisons to chance

```{r }
e1_data_trained <- subset(e1data, Condition == "Trained") %>%
  filter(Time == "0-1 s")
e1_data_novel <- subset(e1data, Condition == "Novel") %>%
  filter(Time == "0-1 s")
```

Time bin 1.

```{r eval=FALSE}
t.test(e1_data_trained$DiffScore, mu = 0, alternative = "two.sided")
cohensD(e1_data_trained$DiffScore, mu = 0)
t.test(e1_data_novel$DiffScore, mu = 0, alternative = "two.sided")
cohensD(e1_data_novel$DiffScore, mu = 0)
```

Time bins 2-4.

```{r eval=FALSE, }
e1_data_trained <- subset(e1data, Condition == "Trained") %>% filter(Time == "bin2")
e1_data_novel <- subset(e1data, Condition == "Novel") %>% filter(Time == "bin2")
t.test(e1_data_trained$DiffScore, mu = 0, alternative = "two.sided")
t.test(e1_data_novel$DiffScore, mu = 0, alternative = "two.sided")

e1_data_trained <- subset(e1data, Condition == "Trained") %>% filter(Time == "bin3")
e1_data_novel <- subset(e1data, Condition == "Novel") %>% filter(Time == "bin3")
t.test(e1_data_trained$DiffScore, mu = 0, alternative = "two.sided")
t.test(e1_data_trained$DiffScore, mu = 0, alternative = "two.sided")

e1_data_trained <- subset(e1data, Condition == "Trained") %>% filter(Time == "bin4")
e1_data_novel <- subset(e1data, Condition == "Novel") %>% filter(Time == "bin4")
t.test(e1_data_novel$DiffScore, mu = 0, alternative = "two.sided")
t.test(e1_data_novel$DiffScore, mu = 0, alternative = "two.sided")

e1_data_trained <- subset(e1data, Condition == "Trained") %>% filter(Time == "bin5")
e1_data_novel <- subset(e1data, Condition == "Novel") %>% filter(Time == "bin5")
t.test(e1_data_novel$DiffScore, mu = 0, alternative = "two.sided")
t.test(e1_data_novel$DiffScore, mu = 0, alternative = "two.sided")
```

# Experiment 2 (Grasp + Name)

Select the data from Experiment 2.
```{r }
e2data <- subset(dflong, Experiment == "Experiment 2")
head(e2data)
```


### Descriptive statistics

Compute the summary descriptive statistics for each time bin.
```{r echo=FALSE}
# Split by time bin
e2data %>% 
  group_by(Condition, Time) %>%
  get_summary_stats(DiffScore,type = "mean_sd")

# Collapsed across time bins
df %>%
  filter(Experiment == "Experiment 2") %>%
  group_by(Condition) %>%
  get_summary_stats(dftrial,type = "mean_sd")
```

### Normality

Perform the Shapiro-Wilk test of normality.
```{r echo=FALSE}
#Normality
e2data %>%
  group_by(Condition, Time) %>%
  shapiro_test(DiffScore)
```

Draw the histograms of the data.
```{r echo=FALSE, warning=FALSE}
p <- gghistogram(e2data, x = "DiffScore",
                 ggtheme = theme_pubclean(),
                 add = "mean", rug = TRUE, bins = "8",
                 color = "Condition", fill = "Condition", alpha = .2,
                 palette = c("#00AFBB", "#E7B800"),
                 xlab = "Difference Score") +
          facet_grid(Condition ~ Time, labeller = "label_both")

p + 
  font("x.text", size = 6.5) 
```


Draws the correlation between the data and the normal distribution.
```{r echo=FALSE, warning=FALSE}
ggqqplot(e2data, "DiffScore", ggtheme = theme_pubclean()) +
          facet_grid(Condition ~ Time, labeller = "label_both")
```

### GLMM (resubmission)

```{r}
me2.fit1 <- lmer(DiffScore ~ Condition + (1|Subject), data = e2data, REML = FALSE)
me2.fit2 <- lmer(DiffScore ~ Condition+Time + (1|Subject), data = e2data, REML = FALSE)
me2.fit3 <- lmer(DiffScore ~ Condition*Time + (1|Subject), data = e2data, REML = FALSE)
anova(me2.fit1,me2.fit2)
anova(me2.fit2,me2.fit3)
```

```{r}
anova(me2.fit1)
summary(me2.fit1)
shapiro.test(residuals(me2.fit3))
confint(me2.fit1)

broom.mixed::tidy(me2.fit1, effects = "fixed") %>%
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

Residuals.

```{r eval=FALSE, include=FALSE}
library(broom.mixed)

m <- me2.fit1

df.plot = m %>% 
  augment() %>% 
  clean_names() 

# residual plot
ggplot(df.plot, aes(x = fitted, y = resid)) + 
  geom_point()

# density of residuals 
ggplot(df.plot, aes(x = resid)) + 
  stat_density(geom = "line")

# QQ plot 
ggplot(df.plot, aes(sample = resid)) + 
  geom_qq() + 
  geom_qq_line()
```

```{r}
prede2 <- predict(me2.fit1)
```

Make a summary table 
```{r}
anova(me2.fit1) %>% 
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

```{r}
tab_model(me2.fit1)
```

### ANOVA (submission)

A repeated-measures ANOVA with:
* $condition$ as a within-subject factor
* $test bin$ (0-1 sec v. 1-2 sec v. 2-3 sec v. 3-4 sec) as a within-subject factor

```{r echo=FALSE, warning=FALSE}
#Run the analysis
e2bins1to4 <- e2data %>%
  filter(Time != "bin5")

ae2 <- aov_car(DiffScore ~ Time*Condition + Error(Subject/Time*Condition), 
                   data = e2bins1to4)
#Display the results
summary(ae2)
eta_sq(ae2, partial = TRUE)
```

#### Figures

```{r }
e2plot <- e2data 

e2plot$Time <- factor(e2plot$Time, 
                      levels = c("0-1 s", "1-2 s", "2-3 s", "3-4 s", "4-5 s"))

e2s <- e2plot %>%
  group_by(Condition, Time) %>%
  get_summary_stats(DiffScore,type = "mean_se")
  
e2s$Time <- factor(e2s$Time)
```

```{r }
library(ggrepel)
library(grid)
grob <- grobTree(textGrob("Object targeted by the action", x=.6,  y=.9, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
grob2 <- grobTree(textGrob("Distractor", x=.86,  y=.1, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
```
 
##### Line plots

```{r echo=FALSE}
pe2.l <- ggplot(data = e2s,aes(x=Time, y = mean, color=Condition,group=Condition)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20),
                plot.subtitle = element_text(size = 16, face = "italic")) +
  geom_point(size=3) +
  geom_line(aes(linetype=Condition),size=1) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  scale_fill_manual(values = c("steelblue", "orange")) +
  scale_color_manual(values = c("steelblue", "orange")) +
  scale_y_continuous(name="Difference score", limits=c(-.8, .8)) +
  ggtitle(label = "Experiment 2", subtitle = "Grasping + Naming") +
  annotation_custom(grob) +
  annotation_custom(grob2)

pe2.l
```

##### Box plots
```{r}
b2 <- ggplot(data = e2plot, aes(x=Time, y=DiffScore)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20)) +
  geom_boxplot(aes(fill=Condition), position = position_dodge(.9), alpha = .05) +
  geom_jitter(aes(color=Condition),position = position_jitterdodge(.15)) +
  scale_y_continuous(name="Difference score", limits=c(-1.25, 1.25)) +
  scale_fill_manual(values = c("steelblue", "orange")) +
  scale_color_manual(values = c("steelblue", "orange")) +
  ggtitle("  \n ")

b2
```



### Follow-up tests

#### Difference scores collapsed across time

```{r echo=FALSE}
#Normality
df %>%
  filter(Experiment == "Experiment 2") %>%
  group_by(Condition) %>%
  shapiro_test(dftrial)
```

#### Comparisons to chance

```{r }
#Trained condition
t.test(df$dftrial[df$Condition == "Trained" & df$Experiment == "Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(df$dftrial[df$Condition == "Trained" & df$Experiment == "Experiment 2"], mu = 0)

#Novel condition
t.test(df$dftrial[df$Condition == "Novel" & df$Experiment == "Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(df$dftrial[df$Condition == "Novel" & df$Experiment == "Experiment 2"], mu = 0)
```

# Comparison between Experiments 1-2

## GLMM (resubmission)

```{r}
e1e2data <- dflong %>%
  filter(Experiment == "Experiment 1" | Experiment == "Experiment 2") %>%
  filter(Time == "0-1 s")
```

```{r}
mfit.e12 <- lmer(DiffScore ~ Condition * Experiment + (1|Subject), data = e1e2data, REML = FALSE)
anova(mfit.e12)
summary(mfit.e12)
confint(mfit.e12)

broom.mixed::tidy(mfit.e12, effects = "fixed") %>%
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

Residuals.

```{r}
shapiro.test(residuals(mfit.e12))
```


Make a summary table 
```{r}
anova(mfit.e12) %>% 
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

```{r}
tab_model(mfit.e12)
```

## Omnibus ANOVA (submission)

```{r echo=FALSE, message=FALSE, warning=FALSE}
e1e2anova <- subset(dflong, 
                    (Experiment == "Experiment 1" | Experiment == "Experiment 2")) %>%
  filter(Time != "bin5")
        
ae1e2<-aov_car((DiffScore ~ Time*Condition*Experiment 
                + Error(Subject/Time*Condition) + Experiment), 
  data = e1e2anova)

summary(ae1e2)
eta_sq(ae1e2, partial = TRUE)
```

### Separate ANOVAs by time bin

Test bin 1 (0-1 s).
```{r}
#ANOVA
ae1e2b1 <- aov_car((DiffScore ~ Condition*Experiment 
                + Error(Subject/Condition) + Experiment), data = e1e2anova%>%filter(Time == "0-1 s"))

summary(ae1e2b1)
eta_sq(ae1e2b1, partial = TRUE)
```

Test bin 2.
```{r}
ae1e2b2 <- aov_car((DiffScore ~ Condition*Experiment + Error(Subject/Condition) + Experiment),
                   data = e1e2anova%>%filter(Time == "1-2 s"))

summary(ae1e2b2)
```

Test bin 3.
```{r}
ae1e2b3 <- aov_car((DiffScore ~ Condition*Experiment + Error(Subject/Condition) + Experiment),
                   data = e1e2anova%>%filter(Time == "2-3 s"))

summary(ae1e2b3)
```

Test bin 4.
```{r}
#ANOVA
ae1e2b4 <- aov_car((DiffScore ~ Condition*Experiment + Error(Subject/Condition) + Experiment),
                   data = e1e2anova%>%filter(Time == "3-4 s"))

summary(ae1e2b4)
```

# Experiment 3 (Name + Grasp)

## Descriptive statistics
Compute the summary descriptive statistics.
```{r echo=FALSE}
e3data %>%
  group_by(Condition, Time) %>%
  get_summary_stats(DiffScore,type = "mean_sd")

# Collapsed across time bins
df %>%
  filter(Experiment == "Experiment 3") %>%
  group_by(Condition) %>%
  get_summary_stats(dftrial,type = "mean_sd")
```

## Normality

Perform the Shapiro-Wilk test of normality.
```{r echo=FALSE}
#Normality
e3data %>%
  group_by(Condition, Time) %>%
  shapiro_test(DiffScore)
```

Draw the histograms of the data.
```{r echo=FALSE, warning=FALSE}
p <- gghistogram(e3data, x = "DiffScore",
                 ggtheme = theme_pubclean(),
                 add = "mean", rug = TRUE, bins = "8",
                 color = "Condition", fill = "Condition", alpha = .2,
                 palette = c("#00AFBB", "#E7B800"),
                 xlab = "Difference Score") +
          facet_grid(Condition ~ Time, labeller = "label_both")

p + 
  font("x.text", size = 6.5) 
```


Draws the correlation between the data and the normal distribution.
```{r echo=FALSE, warning=FALSE}
ggqqplot(e3data, "DiffScore", ggtheme = theme_pubclean()) +
          facet_grid(Condition ~ Time, labeller = "label_both")
```

## GLMM (resubmission)

```{r}
me3.fit1 <- lmer(DiffScore ~ Condition + (1|Subject), data = e3data, REML = FALSE)
me3.fit2 <- lmer(DiffScore ~ Condition+Time + (1|Subject), data = e3data, REML = FALSE)
me3.fit3 <- lmer(DiffScore ~ Condition*Time + (1|Subject), data = e3data, REML = FALSE)
anova(me3.fit1,me3.fit2)
anova(me3.fit2,me3.fit3)
```

```{r}
anova(me3.fit1)
summary(me3.fit1)
confint(me3.fit1)
shapiro.test(residuals(me3.fit1))

broom.mixed::tidy(me3.fit1, effects = "fixed") %>%
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```


Make a summary table 
```{r}
anova(me3.fit1) %>% 
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

```{r}
tab_model(me3.fit1)
```

## ANOVA

A repeated-measures ANOVA with:
* $condition$ (trained v. novel word) as a within-subject factor
* $time$ (test bin 1 v. test bin 2 v. test bin 3 v. test bin 4) as a within-subject factor

```{r echo=FALSE, warning=FALSE}
#Run the analysis
e3anova <- subset(e3data, Time != "bin5")

ae3 <- aov_car(DiffScore ~ Time*Condition + Error(Subject/Time*Condition), 
                   data = e3anova)
#Display the results
summary(ae3)
eta_sq(ae3, partial = TRUE)
```

### Figures

```{r }
e3plot <- e3data 

e3plot$Time <- factor(e3plot$Time, 
                       levels = c("0-1 s","1-2 s","2-3 s", "3-4 s", "4-5 s"))

e3s <- e3plot %>%
  group_by(Condition, Time) %>%
  get_summary_stats(DiffScore,type = "mean_se")
  
e3s$Time <- factor(e3s$Time)
```

```{r }
library(ggrepel)
library(grid)
grob <- grobTree(textGrob("Object targeted by the action", x=.6,  y=.9, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
grob2 <- grobTree(textGrob("Distractor", x=.86,  y=.1, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
```
 
#### Line plots

```{r echo=FALSE}
pe3.l <- ggplot(data = e3s,aes(x=Time, y = mean, color=Condition,group=Condition)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20),
                plot.subtitle = element_text(size = 16, face = "italic")) +
  geom_point(size=3) +
  geom_line(aes(linetype=Condition),size=1) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  scale_fill_manual(values = c("steelblue", "orange")) +
  scale_color_manual(values = c("steelblue", "orange")) +
  scale_y_continuous(name="Difference Score", limits=c(-.8, .8)) +
  ggtitle("Experiment 3", subtitle = "Naming + Grasping") +
  annotation_custom(grob) +
  annotation_custom(grob2)

pe3.l
```

#### Box plots

```{r}
b3 <- ggplot(data = e3data, aes(x=Time, y=DiffScore)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 14)) +
  geom_boxplot(aes(fill=Condition), position = position_dodge(.9), alpha = .05) +
  geom_jitter(aes(color=Condition),position = position_jitterdodge(.15)) +
  scale_y_continuous(name="Difference Score", limits=c(-1.25, 1.25)) +
  scale_fill_manual(values = c("steelblue", "orange")) +
  scale_color_manual(values = c("steelblue", "orange")) +
  ggtitle("  \n ")

b3
```

## Follow-up tests

#### Average over time

Descriptive statistics.
```{r echo=FALSE}
e3datatimeave <-e3data %>%
  group_by(Subject,Condition) %>%
  summarize(avedf = mean(DiffScore, na.rm=T))

e3datatimeave %>%
  group_by(Condition) %>%
  get_summary_stats(avedf, type="mean_sd")
```

```{r echo=FALSE}
#Normality
e3datatimeave %>%
  group_by(Condition) %>%
  shapiro_test(avedf)
```

### Comparisons to chance

```{r }
#Trained condition
t.test(e3datatimeave$avedf[e3datatimeave$Condition == "Trained"], mu = 0, alternative = "two.sided")
cohensD(e3datatimeave$avedf[e3datatimeave$Condition == "Trained"], mu = 0)

#Novel condition
t.test(e3datatimeave$avedf[e3datatimeave$Condition == "Novel"], mu = 0, alternative = "two.sided")
cohensD(e3datatimeave$avedf[e3datatimeave$Condition == "Novel"], mu = 0)
```

```{r }
#Trained condition
t.test(df$dftrial[df$Condition == "Trained" & df$Experiment == "Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(df$dftrial[df$Condition == "Trained" & df$Experiment == "Experiment 3"], mu = 0)

#Novel condition
t.test(df$dftrial[df$Condition == "Novel" & df$Experiment == "Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(df$dftrial[df$Condition == "Novel" & df$Experiment == "Experiment 3"], mu = 0)
```


### Comparison between Experiments 2-3

```{r echo=FALSE, message=FALSE, warning=FALSE}
e2e3data <- subset(dflong, (Experiment == "Experiment 2" | Experiment == "Experiment 3")) %>%
  filter(Time == "0-1 s")
        
ae2e3<-aov_car((DiffScore ~ Condition*Experiment 
                + Error(Subject/Condition) + Experiment), data = e2e3data)

summary(ae2e3)
eta_sq(ae2e3, partial = TRUE)
```


```{r}
e2e3data <- dflong %>%
  filter(Experiment == "Experiment 2" | Experiment == "Experiment 3") %>%
  filter(Time == "0-1 s")
```


```{r}
me23.fit1 <- lmer(DiffScore ~ Condition + (1|Subject), data = e2e3data, REML = FALSE)
me23.fit2 <- lmer(DiffScore ~ Condition + Experiment + (1|Subject), data = e2e3data, REML = FALSE)
me23.fit3 <- lmer(DiffScore ~ Condition * Experiment + (1|Subject), data = e2e3data, REML = FALSE)
anova(me23.fit1, me23.fit2)
anova(me23.fit1, me23.fit3)
```

```{r}
anova(me23.fit3)
summary(me23.fit3)
shapiro.test(residuals(me23.fit3))
```

### Comparison between Experiments 1-3

### GLMM (resubmission)

```{r}
e1e3data <- dflong %>%
  filter(Experiment == "Experiment 1" | Experiment == "Experiment 3") %>%
  filter(Time == "0-1 s")
```


```{r}
me13.fit1 <- lmer(DiffScore ~ Condition + (1|Subject), data = e1e3data, REML = FALSE)
me13.fit2 <- lmer(DiffScore ~ Condition + Experiment + (1|Subject), data = e1e3data, REML = FALSE)
me13.fit3 <- lmer(DiffScore ~ Condition * Experiment + (1|Subject), data = e1e3data, REML = FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
e1e3data <- subset(dflong, (Experiment == "Experiment 1" | Experiment == "Experiment 3")) %>%
  filter(Time == "0-1 s")
        
ae1e3<-aov_car((DiffScore ~ Condition*Experiment 
                + Error(Subject/Condition) + Experiment), 
  data = e1e3data)

summary(ae1e3)
eta_sq(ae1e3, partial = TRUE)
```

# Experiment 4 (Point + Name + Occlude)

```{r }
head(e4data)
```

### Descriptive statistics
Compute the summary descriptive statistics.
```{r echo=FALSE}
e4data %>%
  group_by(Condition, Time) %>%
  get_summary_stats(DiffScore,type = "mean_sd")

# Collapsed across time bins
df %>%
  filter(Experiment == "Experiment 4") %>%
  group_by(Condition) %>%
  get_summary_stats(dftrial,type = "mean_sd")
```

### Normality

Perform the Shapiro-Wilk test of normality.
```{r echo=FALSE}
#Normality
df %>%
  filter(Experiment == "Experiment 4") %>%
  group_by(Condition) %>%
  shapiro_test(dftrial)
```

Draw the histograms of the data.
```{r echo=FALSE, warning=FALSE}
p <- gghistogram(e4data, x = "DiffScore",
                 ggtheme = theme_pubclean(),
                 add = "mean", rug = TRUE, bins = "8",
                 color = "Condition", fill = "Condition", alpha = .2,
                 palette = c("#00AFBB", "#E7B800"),
                 xlab = "Difference Score") +
          facet_grid(Condition ~ Time, labeller = "label_both")

p + font("x.text", size = 6.5) 
```


Draws the correlation between the data and the normal distribution.
```{r echo=FALSE, warning=FALSE}
ggqqplot(e4data, "DiffScore", ggtheme = theme_pubclean()) +
          facet_grid(Condition ~ Time, labeller = "label_both")
```

### GLMM (resubmission)

```{r}
me4.fit1 <- lmer(DiffScore ~ Condition + (1|Subject), data = e4data, REML = FALSE)
me4.fit2 <- lmer(DiffScore ~ Condition+Time + (1|Subject), data = e4data, REML = FALSE)
me4.fit3 <- lmer(DiffScore ~ Condition*Time + (1|Subject), data = e4data, REML = FALSE)
```

```{r echo=FALSE, warning=FALSE}
ae4 <- aov_car(DiffScore ~ Time*Condition + Error(Subject/Time*Condition), data = e4data)
summary(ae4)
eta_sq(ae4, partial = TRUE)
```


### ANOVA (submission)

A repeated-measures ANOVA with:
* $condition$ (trained v. novel word) as a within-subject factor
* $time$ (test bin 1 v. test bin 2 v. test bin 3 v. test bin 4) as a within-subject factor

```{r echo=FALSE, warning=FALSE}
#Run the analysis
ae4 <- aov_car(DiffScore ~ Time*Condition + Error(Subject/Time*Condition), data = e4data)

#Display the results
summary(ae4)
eta_sq(ae4, partial = TRUE)
```


### Figures

```{r }
e4plot <- e4data

e4plot$Time <- factor(e4plot$Time, 
                       levels = c("0-1 s","1-2 s",
                                  "2-3 s", "3-4 s", "4-5 s"))

e4s <- e4plot %>%
  group_by(Condition, Time) %>%
  get_summary_stats(DiffScore,type = "mean_se")
  
e4s$Time <- factor(e4s$Time)
```

```{r }
library(ggrepel)
library(grid)
grob <- grobTree(textGrob("Object targeted by the action", x=.6,  y=.9, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
grob2 <- grobTree(textGrob("Distractor", x=.86,  y=.1, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
```

#### Line plots

```{r echo=FALSE}
pe4.l <- ggplot(data = e4s,aes(x=Time, y = mean, color=Condition,group=Condition)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20),
                 plot.subtitle = element_text(size = 16, face = "italic")) +
  geom_point(size=3) +
  geom_line(aes(linetype=Condition),size=1) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +#,position=position_dodge(.9)) +
  scale_fill_manual(values = c("steelblue", "orange")) +
  scale_color_manual(values = c("steelblue", "orange")) +
  scale_y_continuous(name="Difference Score", limits=c(-.8, .8)) +
  ggtitle(label = "Experiment 4", subtitle = "Pointing + Naming + Occlusion + Objects' location swap") +
  annotation_custom(grob) +
  annotation_custom(grob2)

pe4.l
```

#### Box plots

```{r}
b4 <- ggplot(data = e4data, aes(x=Time, y=DiffScore)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20)) +
  geom_boxplot(aes(fill=Condition), position = position_dodge(.9), alpha = .05) +
  geom_jitter(aes(color=Condition),position = position_jitterdodge(.15)) +
  scale_y_continuous(name="Difference Score", limits=c(-1.25, 1.25)) +
  scale_fill_manual(values = c("steelblue", "orange")) +
  scale_color_manual(values = c("steelblue", "orange")) +
  ggtitle("  \n ")

b4

```

### Folluw-up tests (resubmission)

#### Average over time

Descriptive statistics.
```{r echo=FALSE}
e4datatimeave <-e4data %>%
  group_by(Subject,Condition) %>%
  summarize(avedf = mean(DiffScore, na.rm=T))

e4datatimeave %>%
  group_by(Condition) %>%
  get_summary_stats(avedf, type="mean_sd")
```

```{r echo=FALSE}
#Normality
e4datatimeave %>%
  group_by(Condition) %>%
  shapiro_test(avedf)
```

#### Comparisons to chance

```{r }
#Trained condition
t.test(df$dftrial[df$Condition == "Trained" & df$Experiment == "Experiment 4"], mu = 0, alternative = "two.sided")
cohensD(df$dftrial[df$Condition == "Trained" & df$Experiment == "Experiment 4"], mu = 0)

#Novel condition
t.test(df$dftrial[df$Condition == "Novel" & df$Experiment == "Experiment 4"], mu = 0, alternative = "two.sided")
cohensD(df$dftrial[df$Condition == "Novel" & df$Experiment == "Experiment 4"], mu = 0)
```


### Follow-up tests (submission)

#### Comparisons between conditions

To solve the interaction between $condition x time$, we conducted separate paired samples t tests within each test bin.

```{r }
t.test(DiffScore ~ Condition, data = e4data %>% filter(Time == "0-1 s"), paired = TRUE)
cohensD(DiffScore ~ Condition, data = e4data %>% filter(Time == "0-1 s"), method = "paired")
```

```{r }
t.test(DiffScore ~ Condition, data = e4data %>% filter(Time == "1-2 s"), paired = TRUE)
cohensD(DiffScore ~ Condition, data = e4data %>% filter(Time == "1-2 s"), method = "paired")
```

```{r }
t.test(DiffScore ~ Condition, data = e4data %>% filter(Time == "2-3 s"), paired = TRUE)
cohensD(DiffScore ~ Condition, data = e4data %>% filter(Time == "2-3 s"), method = "paired")
```

#### Comparisons to chance


### Comparision between Experiments 1 v. 4 

```{r}
e1e4data <- dflong %>%
  filter(Experiment == "Experiment 1" | Experiment == "Experiment 4") %>%
  filter(Time == "0-1 s")
```


```{r}
me14.fit1 <- lmer(DiffScore ~ Condition + (1|Subject), data = e1e4data, REML = FALSE)
me14.fit2 <- lmer(DiffScore ~ Condition + Experiment + (1|Subject), data = e1e4data, REML = FALSE)
me14.fit3 <- lmer(DiffScore ~ Condition * Experiment + (1|Subject), data = e1e4data, REML = FALSE)
```

# Manuscript figure

```{r}
e1 <- ggarrange(pe1.l, b1,
                ncol = 2, widths = c(1.5,1),
                common.legend = TRUE, legend = "bottom")

e2 <- ggarrange(pe2.l, b2,
                ncol = 2, widths = c(1.5,1),
                common.legend = TRUE, legend = "bottom")
      
e3 <- ggarrange(pe3.l,b3,
          ncol = 2, widths = c(1.5,1),
          common.legend = TRUE, legend = "bottom")

e4 <- ggarrange(pe4.l,b4,
                ncol = 2, widths = c(1.5,1),
                common.legend = TRUE, legend = "bottom")
```

```{r echo=FALSE}
figure2 <- ggarrange(e1, e2, e3, e4,
          ncol = 1,
          common.legend = TRUE, legend = "bottom")

figure2
```

```{r include=FALSE}
ggsave("plots/figure2.png", plot = last_plot(), width = 35, height = 45, units = c("cm"))
```

