---
title: "POINT"
author: "blinded"
output: html_document
---

Libraries and set up.

```{r message=FALSE, warning=FALSE, , paged.print=FALSE, include=FALSE}
library(readxl)
library(tidyverse)
library(ggpubr)
library(rstatix)
```

Read in individual data from data/dataindividual
```{r warning=FALSE, include=FALSE}
# Set the path
setwd("~/Documents/GitHub/pointa/data/dataindividual/")
#Get file names of individual data files
my_files <- list.files(pattern = "xlsx$")
# Read each excel file into a list
listExcel = lapply(my_files, read_excel)
# Concatenate the data in each file into one combined data frame
results = do.call(rbind.data.frame, listExcel)
rm(listExcel)
```

Recode 9999 to missing data.
```{r}
results[results==9999] <- NA
```

# AOI Hits

Compute AOI hits.

```{r}
#Define AOIs
aoileft = c(5,540,810,1075)
aoiright = c(1110,540,1915,1075)
```

```{r}
results <- results %>%
  mutate(gazex = as.numeric(gazex)) %>%
  mutate(gazey = as.numeric(gazey))
```

Compute AOI hits for the object targeted by the action:
tg (object targeted by the action), dt (distractor object)

```{r}
#Compute AOI hits
results <- results %>%
  mutate(tghit = ifelse((locactiontarget == "left" | locactiontarget == "L"),
                            (ifelse((gazex >= aoileft[1] & gazex <= aoileft[3] & gazey >= aoileft[2] & gazey <= aoileft[4]),1,0)),
                            (ifelse((locactiontarget == "right" | locactiontarget == "R"),
                               ifelse((gazex >= aoiright[1] & gazex <= aoiright[3] & gazey >= aoiright[2] & gazey <= aoiright[4]),1,0),"?")))) %>%
  mutate(dthit = ifelse((locactiontarget == "right" | locactiontarget == "R"),
                            (ifelse((gazex >= aoileft[1] & gazex <= aoileft[3] & gazey >= aoileft[2] & gazey <= aoileft[4]),1,0)),
                            (ifelse((locactiontarget == "left" | locactiontarget == "L"),
                               ifelse((gazex >= aoiright[1] & gazex <= aoiright[3] & gazey >= aoiright[2] & gazey <= aoiright[4]),1,0),"?")))) %>%
  mutate(missingdata = ifelse((is.na(gazex) == 1 & is.na(gazey) == 1), 1, 0))
```


```{r}
results <- results %>%
  mutate(tghit = as.numeric(tghit)) %>%
  mutate(dthit = as.numeric(dthit))
```

Add experiment.
```{r}
results <- results %>%
  mutate(experiment = ifelse((ID<17),1,ifelse((ID<33),2,(ifelse(ID<49,3,4)))))
```

Compute difference scores.
```{r}
binary <- results %>%
  group_by(experiment,ID,trial,trialtype,timebin) %>%
  summarise(sumtghits = sum(tghit,na.rm=TRUE), 
            sumdthits = sum(dthit,na.rm=TRUE), 
            sumhits = sumtghits+sumdthits,countna = sum(missingdata),
            .groups = "keep") %>%
  mutate(df = (sumtghits-sumdthits)/(sumtghits+sumdthits))

# Compute difference scores
df <- binary %>%
  select(experiment, ID, trial, trialtype, timebin, df, countna) %>%
  pivot_wider(names_from = "timebin", 
                    values_from = c("df","countna"), 
                    values_fn = unique) %>%
  mutate(totalna = 
           countna_bin1 + countna_bin2 + countna_bin3 + countna_bin4 + countna_bin5) %>%
  mutate(attendancetest = 1-(totalna/300)) 
```

# Data exclusion

```{r}
setwd("~/Documents/GitHub/pointa/data/")
attendancebeforetest <- read_excel("attendancebeforetest.xlsx")
df <- merge(df,attendancebeforetest, by=c("ID","trial","experiment"))
binary <- merge(binary,attendancebeforetest, by=c("ID","trial","experiment"))
```

Exclude trials with <50% screen attendance.
```{r}
df <- df %>%
  mutate(inclusion = ifelse((attendance == 1),1,0))
```

# Screen attendance

```{r}
aux <- df %>%
  filter(inclusion == 1) %>%
  group_by(experiment,ID,trialtype) %>%
  get_summary_stats(attendancetest, type = "mean_sd")

aux %>%
  group_by(experiment,trialtype) %>%
  summarise(gmean = round(mean(mean), digits = 2),
            gmedian = round(median(mean), digits = 2),
            gsd = round(sd(mean), digits = 2),
            gmin = round(min(mean), digits = 2),
            gmax = round(max(mean), digits = 2),
            .groups = "keep")
```


# Trial numbers

Included trials.

```{r}
df %>%
  filter(experiment == 4 & trialtype == "Untrained") %>%
  select(ID, trial, inclusion) %>%
  #group_by(ID) %>%
  summarise(sumincl = sum(inclusion))
```

```{r}
aux <- df %>%
  group_by(experiment,ID,trialtype) %>%
  summarize(trialnumber = sum(inclusion,na.rm=TRUE), groups = "keep")

aux %>%
  group_by(experiment,trialtype) %>%
  get_summary_stats(trialnumber, type = "mean_sd")
```

# Difference scores

Compute average stats for each participant.
Inlcude only trials with a minimum 50% onscreen data during both pretest and test.

```{r}
meandf <- df %>%
  filter(inclusion == 1) %>%
  group_by(experiment,ID,trialtype) %>%
  summarize(bin1 = mean(df_bin1,na.rm=TRUE),
            bin2 = mean(df_bin2,na.rm=TRUE), 
            bin3 = mean(df_bin3,na.rm=TRUE),
            bin4 = mean(df_bin4,na.rm=TRUE),
            bin5 = mean(df_bin5,na.rm=TRUE), .groups = "keep")
```

```{r}
colnames(meandf)[1] <- "Experiment"
colnames(meandf)[2] <- "Subject"
colnames(meandf)[3] <- "Condition"
```

```{r}
meandf %>%
  group_by(Experiment,Condition) %>%
  get_summary_stats(bin1, bin2, bin3, bin4, type="mean_sd")
```

Save the data.
```{r}
library(openxlsx)

meandf$Condition <- factor(meandf$Condition, 
                           levels = c("Trained", "Untrained"),
                           labels = c("Trained", "Novel"))

write.xlsx(meandf, "data/datadftest.xlsx", sheetName = "data")
```

