---
title: "Complementary analyses | POINT | Nonverbal action interpretation guides novel word disambiguation in 12-month-olds"
author: /
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---


# Data structure

## Difference scores

data_differencescores.xlsx contains:

* $Experiment$       -- Experiment 1, Experiment 2, Experiment 3, Experiment 4

* $ID$               -- unique ID identifying each participant

* $Condition$        -- word heard at test (trained v. novel)

* $Namingaction_mean$     -- average difference score in the naming phase (Experiment 1, 2, 4) or still action phase (Experiment 4)

* $Pretest_mean$          -- average difference score in the pretest phase

## First looks

data_firstlooks.xlsx contains:


# Libraries and set up

```{r message=FALSE, warning=FALSE, , paged.print=FALSE}
library(tidyverse)
library(readxl)
library(rstatix)
library(ggpubr)
library(emmeans)
library(afex)
library(sjstats)
library(lsr)
```

# Naming 

Load the data.
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
d <- read_excel("data/datadfnamingpretest.xlsx",sheet="data")
```

Prepare the dataset.
```{r }
#Convert Condtition as factor, recode the levels as: Trained, Novel
d$Condition <- factor(d$Condition,
                                levels = c("Trained","Novel"),
                                labels = c("Trained","Novel"))

#Convert Id, Experiment as factor
d$Id <- factor(d$Id)
d$Experiment <- factor(d$Experiment)

#Check the data structure
str(d)
```

```{r}
select_vars1 <- c("Namingaction_trial1","Namingaction_trial2","Namingaction_trial3","Namingaction_trial4")
select_vars2 <- c("Pretest_trial1","Pretest_trial2","Pretest_trial3","Pretest_trial4")

d <- d %>%
  mutate(meannaming = rowMeans(select(., select_vars1),na.rm = TRUE)) %>%
  mutate(meanpretest= rowMeans(select(., select_vars2),na.rm = TRUE))
```

## Descriptive statistics

Compute means and standard deviations for each experiment. 
```{r}
d %>%
  group_by(Experiment,Id) %>%
  summarise(meanave = mean(meannaming), .groups = "keep") %>%
  group_by(Experiment) %>%
  get_summary_stats(meanave, type = "mean_sd")
```

Check whether the data is normally distributed.
```{r}
d %>%
  group_by(Experiment,Id) %>%
  summarise(meanave = mean(meannaming), .groups = "keep") %>%
  group_by(Experiment) %>%
  shapiro_test(meanave)
```

## ANOVA [Experiments 1, 2, 4]

```{r}
daov <- d %>% 
  group_by(Experiment,Id) %>%
  summarise(meanave = mean(meannaming), .groups = "keep")
```

ANOVA.
```{r}
anaming<-aov_car((meanave ~ Experiment + Error(Id)), 
                 data = daov %>%filter(Experiment != "Experiment 3"))

summary(anaming)
eta_sq(anaming, partial = TRUE)
```

### Comparisons to chance

Experiment 1.
```{r}
aux <- daov %>% filter(Experiment == "Experiment 1")
t.test(aux$meanave, mu = 0, alternative = "two.sided")
cohensD(aux$meanave, mu = 0)
```

Experiment 2.
```{r}
aux <- daov %>% filter(Experiment == "Experiment 2")
t.test(aux$meanave, mu = 0, alternative = "two.sided")
cohensD(aux$meanave, mu = 0)
```

Experiment 3.
```{r }
aux <- daov %>% filter(Experiment == "Experiment 3")
t.test(aux$meanave, mu = 0, alternative = "two.sided")
cohensD(aux$meanave, mu = 0)
```

Experiment 4.
```{r}
aux <- daov %>% filter(Experiment == "Experiment 4")
t.test(aux$meanave, mu = 0, alternative = "two.sided")
cohensD(aux$meanave, mu = 0)
```

## Figures

```{r }
library(ggrepel)
library(grid)
grob <- grobTree(textGrob("Object targeted by the action", x=.5,  y=.95, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
grob2 <- grobTree(textGrob("Distractor", x=.8,  y=.1, hjust=0,
  gp=gpar(col="gray50", fontsize=16)))
```

```{r}
namingdata <- d
ppnaming <- ggplot(data = namingdata, aes(x=Experiment, y=meannaming)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20)) +
  geom_boxplot(position = position_dodge(.9), alpha = .05, width =.5) +
  geom_jitter(aes(color=Condition), position = position_jitter(.15), size = 1.5, alpha = .55) +
  scale_y_continuous(name="Difference score", limits=c(-1.25, 1.25)) +
  scale_fill_manual(values = c("black", "orange")) +
  scale_color_manual(values = c("black", "orange")) +
  stat_summary(fun.data = mean_se, fill="red", color = "blue", shape=18, size = 1.5) +
  ggtitle("Attention during naming") +
  annotation_custom(grob) +
  annotation_custom(grob2)

ppnaming
```

# Pretest

## Descriptive statistics

Compute means and standard deviations for each experiment. 
```{r}
d %>%
  group_by(Experiment,Id) %>%
  summarise(meanave = mean(meanpretest), .groups = "keep") %>%
  group_by(Experiment) %>%
  get_summary_stats(meanave, type = "mean_sd")
```

Check whether the data is normally distributed.
```{r}
d %>%
  group_by(Experiment,Id) %>%
  summarise(meanave = mean(meanpretest), .groups = "keep") %>%
  group_by(Experiment) %>%
  shapiro_test(meanave)
```

## ANOVA

```{r}
daovpretest <- d %>% 
  group_by(Experiment,Id) %>%
  summarise(meanave = mean(meanpretest), .groups = "keep")
```

```{r}
#Convert Time as factor
apretest<-aov_car((meanave ~ Experiment + Error(Id)), 
  data = daovpretest)

summary(apretest)
eta_sq(apretest, partial = TRUE)
```

### Follow-ups
```{r}
emmeans(apretest, "Experiment", contr = "pairwise", model = "multivariate")
```

### Comparisons to chance
```{r}
preteste1 <- daovpretest %>% filter(Experiment == "Experiment 1")
preteste2 <- daovpretest %>% filter(Experiment == "Experiment 2")
preteste3 <- daovpretest %>% filter(Experiment == "Experiment 3")
preteste4 <- daovpretest %>% filter(Experiment == "Experiment 4")
```

Experiment 1.

```{r}
aux <- daovpretest %>% filter(Experiment == "Experiment 1")
t.test(aux$meanave, mu = 0, alternative = "two.sided")
cohensD(aux$meanave, mu = 0)
```

Experiment 2.

```{r}
aux <- daovpretest %>% filter(Experiment == "Experiment 2")
t.test(aux$meanave, mu = 0, alternative = "two.sided")
cohensD(aux$meanave, mu = 0)
```

Experiment 3.

```{r}
aux <- daovpretest %>% filter(Experiment == "Experiment 3")
t.test(aux$meanave, mu = 0, alternative = "two.sided")
cohensD(aux$meanave, mu = 0)
```

Experiment 4.

```{r}
aux <- daovpretest %>% filter(Experiment == "Experiment 4")
t.test(aux$meanave, mu = 0, alternative = "two.sided")
cohensD(aux$meanave, mu = 0)
```

## Figures

```{r}
pretestdata <- d
ppretest <- ggplot(data = pretestdata, aes(x=Experiment, y=meanpretest)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20)) +
  geom_boxplot(position = position_dodge(.9), alpha = .05, width =.5) +
  geom_jitter(aes(color=Condition), position = position_jitter(.15), alpha = .55) +
  scale_y_continuous(name="Difference score", limits=c(-1.25, 1.25)) +
  scale_fill_manual(values = c("black", "orange")) +
  scale_color_manual(values = c("black", "orange")) +
  stat_summary(fun.data = mean_se, fill="blue", color = "blue", shape=18, size = 1.5) +
  annotation_custom(grob) +
  annotation_custom(grob2) +
  ggtitle("Attention during pretest")

ppretest
```

# First looks

Load the data.
```{r }
# Load the data
dfirstlooks <- read_excel("data/datafirstlooks.xlsx",sheet="data")
```

Prepare the dataset.
```{r }
#Convert Condtition as factor, recode the levels as: Trained, Novel
dfirstlooks$Condition <- factor(dfirstlooks$Condition,
                                levels = c("Trained","Novel"),
                                labels = c("Trained","Novel"))

#Convert Id, Experiment as factor
dfirstlooks$Id <- factor(dfirstlooks$Id)
dfirstlooks$Experiment <- factor(dfirstlooks$Experiment)

#Check the data structure
str(dfirstlooks)
```

### Summary statistics

```{r echo=FALSE}
dfirstlooks %>%
  group_by(Experiment, Condition) %>%
  get_summary_stats(Proportion,type = "mean_sd")
```

```{r echo=FALSE}
dfirstlooks %>%
  group_by(Experiment,Condition) %>%
  shapiro_test(Proportion)
```

```{r echo=FALSE}
dfirstlooks %>%
  group_by(experiment,trialtype) %>%
  get_summary_stats(ptarget,type = "mean_sd")
```

### Figures

```{r}
dfirstlooks <- resultsfirstlooks
m <- dfirstlooks %>%
  group_by(Experiment, Condition) %>%
  get_summary_stats(Proportion,type = "mean_se")

m <- dfirstlooks %>%
  group_by(experiment, trialtype) %>%
  get_summary_stats(ptarget,type = "mean_se")

flookp <- ggplot(data = dfirstlooks, aes(x=Experiment, y=Proportion)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20)) +
  geom_boxplot(aes(fill=Condition), position = position_dodge(0.75),
               alpha = .05, width = .5) +
  geom_dotplot(aes(fill=Condition),
               binaxis='y', stackdir='center',
               stackratio=0.75, dotsize = 0.75, 
               position = position_dodge(.75)) +
  scale_y_continuous(name="Proportion of looks at the action target",
                     limits=c(-.05, 1.05)) +
  scale_fill_manual(values = c("black", "orange")) +
  scale_color_manual(values = c("black", "orange")) +
  stat_summary(fun.data = mean_se, fill="blue", color = "blue",
               mapping = aes(group = Condition), position=position_dodge(0.75), shape=18, size = 2) +
  ggtitle("First looks")

flookp
```

```{r}
flookp <- ggplot(data = dfirstlooks, aes(x=experiment, y=ptarget)) +
  theme_light() +
          theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="gray75"),
                panel.grid.major.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=16),
                axis.text.x = element_text(size=16),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20)) +
  geom_boxplot(aes(fill=trialtype), position = position_dodge(0.75),
               alpha = .05, width = .5) +
  geom_dotplot(aes(fill=trialtype),
               binaxis='y', stackdir='center',
               stackratio=0.75, dotsize = 0.75, 
               position = position_dodge(.75)) +
  scale_y_continuous(name="Proportion of looks at the action target",
                     limits=c(-.05, 1.05)) +
  scale_fill_manual(values = c("black", "orange")) +
  scale_color_manual(values = c("black", "orange")) +
  stat_summary(fun.data = mean_se, fill="blue", color = "blue",
               mapping = aes(group = trialtype), position=position_dodge(0.75), shape=18, size = 2) +
  ggtitle("First looks")

flookp
```


### Analysis

```{r}
firstlooke1 <- subset(firstlook, 
                    (Experiment == "Experiment 1"))

firstlooke2 <- subset(firstlook, 
                    (Experiment == "Experiment 2"))

firstlooke3 <- subset(firstlook, 
                    (Experiment == "Experiment 3"))

firstlooke4 <- subset(firstlook, 
                    (Experiment == "Experiment 4"))
```

```{r}
firstlooke1 <- subset(resultsfirstlooks, 
                    (experiment == 1))

firstlooke2 <- subset(resultsfirstlooks, 
                    (experiment == 2))

firstlooke3 <- subset(resultsfirstlooks, 
                    (experiment == 3))

firstlooke4 <- subset(resultsfirstlooks, 
                    (experiment == 4))
```


```{r warning=FALSE}
wt <- wilcox.test(ptarget ~ trialtype, data = firstlooke3, alternative = "two.sided",
                  paired = TRUE,
                  conf.int = TRUE, conf.level = 0.95, exact = TRUE)
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```

Comparisons across conditions within each experiment.

Experiment 1.

```{r warning=FALSE}
wt <- wilcox.test(Proportion ~ Condition, data = firstlooke1, alternative = "two.sided",
                  paired = TRUE,
                  conf.int = TRUE, conf.level = 0.95, exact = TRUE)
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```

Experiment 2.
```{r}
t.test(Proportion ~ Condition, data = firstlooke2, paired = TRUE)
```

Experiment 3.
```{r warning=FALSE}
wt <- wilcox.test(Proportion ~ Condition, data = firstlooke3, alternative = "two.sided",
                  paired = TRUE,
                  conf.int = TRUE, conf.level = 0.95, exact = TRUE)
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```

Experiment 4.
```{r warning=FALSE}
wt <- wilcox.test(Proportion ~ Condition, data = firstlooke4, alternative = "two.sided",
                  paired = TRUE,
                  conf.int = TRUE, conf.level = 0.95, exact = TRUE)
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```

#### Comparisons to chance
##### Trained words
Experiment 1.
```{r warning=FALSE}
aux <- firstlooke1 %>% filter(Condition == "Trained")
wt <- wilcox.test(aux$Proportion, mu = 0.5, data = firstlooke1, alternative = "two.sided")
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```

Experiment 2.
```{r}
aux <- firstlooke2 %>% filter(Condition == "Trained")
t.test(aux$Proportion, mu = 0.5, alternative = "two.sided")
```

Experiment 3.
```{r warning=FALSE}
aux <- firstlooke3 %>% filter(Condition == "Trained")
wt <- wilcox.test(aux$Proportion, mu = 0.5, data = firstlooke1, alternative = "two.sided")
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```

Experiment 4.
```{r warning=FALSE}
aux <- firstlooke4 %>% filter(Condition == "Trained")
wt <- wilcox.test(aux$Proportion, mu = 0.5, data = firstlooke1, alternative = "two.sided")
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```

##### Novel word

Experiment 1.
```{r}
aux <- firstlooke1 %>% filter(Condition == "Novel")
t.test(aux$Proportion, mu = 0.5, alternative = "two.sided")
```

Experiment 2.
```{r}
aux <- firstlooke2 %>% filter(Condition == "Novel")
t.test(aux$Proportion, mu = 0.5, alternative = "two.sided")
```

Experiment 3.
```{r warning=FALSE}
aux <- firstlooke3 %>% filter(Condition == "Novel")
wt <- wilcox.test(aux$Proportion, mu = 0.5, alternative = "two.sided")
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```

Experiment 4.
```{r warning=FALSE}
aux <- firstlooke4 %>% filter(Condition == "Novel")
wt <- wilcox.test(aux$Proportion, mu = 0.5, alternative = "two.sided")
Zstat<-qnorm(wt$p.value/2)
wt
Zstat
```


# Manuscript figure

```{r}
pdfs <- ggarrange(ppnaming, ppretest,
                  labels = c("B", "C"),
                  font.label = list(size = 20, color = "black"),
                  ncol = 2, widths = c(1,1))
```


```{r echo=FALSE}
figure3 <- ggarrange(flookp,NULL,pdfs,
          ncol = 1, heights = c(1, 0.1, 1),
          labels = c("A", " "),
          font.label = list(size = 20, color = "black"),
          common.legend = TRUE, legend = "bottom") +
  theme(legend.text = element_text(color = "red", size = 40))

figure3
```

```{r include=FALSE}
ggsave("plots/figure3.png", plot = last_plot(), width = 35, height = 30, units = c("cm"))
```
