---
title: "POINT"
author: "blinded"
output: html_document
---

Output file: datadftest.xlsx

Libraries and set up.
```{r message=FALSE, warning=FALSE, , paged.print=FALSE, include=FALSE}
library(readxl)
library(tidyverse)
library(ggpubr)
library(rstatix)
library(eyetrackingR)
library(kableExtra)
```

```{r}
library(polypoly)
library(AICcmodavg)
```

Read in individual data from data/dataindividual
```{r warning=FALSE, include=FALSE}
setwd("~/Documents/GitHub/point/data/dataraw/")
results = read_xlsx("datacombined.xlsx",sheet="data", na = "NaN")
```

# Difference scores

Compute difference scores.
```{r}
df <- results %>%
  group_by(experiment,ID,trial,trialtype,timebin,attBeforeTest) %>%
  summarise(sumtghits = sum(tghit,na.rm=TRUE), 
            sumdthits = sum(dthit,na.rm=TRUE), 
            sumcenterhits = sum(centerhit, na.rm = TRUE),
            sumhits = sumtghits+sumdthits,
            countna = sum(missingdata),
            .groups = "keep") %>%
  mutate(df = (sumtghits-sumdthits)/(sumtghits+sumdthits)) %>%
  select(experiment, ID, trial, trialtype, timebin, df, countna, attBeforeTest, sumtghits, sumdthits) %>%
  pivot_wider(names_from = "timebin",  values_from = c("df","countna","sumtghits","sumdthits"), values_fn = unique) %>%
  mutate(
         totalna = (sum = sum(across(starts_with("countna_b")), na.rm = T)),
         totaltg = (sum = sum(across(starts_with("sumtghits_b")), na.rm = T)),
         totaldt = (sum = sum(across(starts_with("sumdthits_b")), na.rm = T)),
         dftrial = (totaltg-totaldt)/(totaltg+totaldt),
         proptrial = totaltg/(totaltg+totaldt),
         onscreenTest = 1-(totalna/300),
         attTest = ifelse(onscreenTest < .5, 0,1),
         inclusion = ifelse(attBeforeTest == 0 | attTest == 0, 0, 1)) 

auxdf <- df %>% ungroup %>% select(experiment,ID,trial, inclusion)
results <- merge(results, auxdf, by = c("experiment","ID","trial"))
remove(auxdf)
```

Compute average difference scores for each participant (by averaging across trials within each condition).
Include only trials with a minimum 50% onscreen data during both pretest and test.

```{r}
meandf <- df %>%
  filter(inclusion == 1) %>%
  group_by(experiment,ID,trialtype) %>%
  summarize(dfbin1 = mean(df_bin1,na.rm=TRUE),
            dfbin2 = mean(df_bin2,na.rm=TRUE), 
            dfbin3 = mean(df_bin3,na.rm=TRUE),
            dfbin4 = mean(df_bin4,na.rm=TRUE),
            dfbin5 = mean(df_bin5,na.rm=TRUE),
            dftrial = mean(dftrial,na.rm=TRUE),
            proptrial = mean(proptrial, na.rm=TRUE),
            .groups = "keep")

colnames(meandf)[1] <- "Experiment"
colnames(meandf)[2] <- "Subject"
colnames(meandf)[3] <- "Condition"
```

```{r}
meandf %>%
  group_by(Experiment,Condition) %>%
  get_summary_stats(dfbin1, dfbin2, dfbin3, dfbin4, dftrial, type="mean_sd")
```

Save the data.
```{r}
library(openxlsx)

meandf$Condition <- factor(meandf$Condition, 
                           levels = c("Trained", "Untrained"),
                           labels = c("Trained", "Novel"))

write.xlsx(meandf, "data/datadftest.xlsx", sheetName = "data")
```

# Screen attendance

Compute screen attendance during the test measurement period.

```{r}
df %>%
  filter(inclusion == 1) %>%
  group_by(experiment,ID,trialtype) %>%
  get_summary_stats(onscreenTest, type = "mean_sd") %>%
  group_by(experiment,trialtype) %>%
  summarise(gmean = round(mean(mean), digits = 2),
            gmedian = round(median(mean), digits = 2),
            gsd = round(sd(mean), digits = 2),
            gmin = round(min(mean), digits = 2),
            gmax = round(max(mean), digits = 2),
            .groups = "keep")
```

# Trial numbers

Included trials.

```{r}
df %>%
  select(experiment,ID,trialtype,trial, inclusion) %>%
  group_by(experiment,trialtype) %>%
  summarise(sumincl = sum(inclusion), n())
```

```{r}
df %>%
  group_by(experiment,ID,trialtype) %>%
  summarize(trialnumber = sum(inclusion,na.rm=TRUE), groups = "keep") %>%
  group_by(experiment,trialtype) %>%
  get_summary_stats(trialnumber, type = "mean_sd")
```

# Complementary analyses

Maker 'results' compatible with 'eyetrackingR', filter out the excluded trials.
AOI : 
timems : time from trial onset

```{r}
results <- results %>%
  mutate(AOI = ifelse(tghit == 1, "target", ifelse(dthit == 1, "distractor", ifelse(centerhit == 1, "center","TrackLoss")))) %>%
  mutate(TrackLoss = ifelse(missingdata == 1, TRUE, FALSE)) %>%
  mutate(ActedObj = ifelse(tghit == 1, TRUE, FALSE)) %>%
  mutate(DistractorObj = ifelse(dthit == 1, TRUE, FALSE)) %>%
  mutate(timems = sample * 1000/60)
```

```{r}
#Include only the trials in which infants attended to the screen for at least 50% of the time
resultsclean <- results %>% filter(inclusion == 1)

data <- make_eyetrackingr_data(resultsclean,
                               participant_column = "ID",
                               trial_column = "trial",
                               time_column = "timems",
                               trackloss_column = "TrackLoss",
                               aoi_columns = c('ActedObj','DistractorObj'),
                               treat_non_aoi_looks_as_missing = TRUE
                               )

# subset to response window post word-onset
response_window <- data %>%
  mutate(Target = trialtype)

response_window <- subset_by_window(data, 
                                    window_start_time = 0, 
                                    window_end_time = 5000, 
                                    rezero = FALSE) %>%
  mutate(Target = trialtype)
```

## Time course plots

```{r}
sizebin = 50 #50 ms

auxd <- make_time_sequence_data(response_window, time_bin_size = sizebin, 
                                 predictor_columns = c("Target"),
                                 aois = c("DistractorObj")
                            )

response_time <- make_time_sequence_data(response_window, time_bin_size = sizebin, 
                                 predictor_columns = c("Target"),
                                 aois = c("ActedObj")
                            ) %>%
  mutate(SamplesDistractor = auxd$SamplesInAOI) %>%
  mutate(SamplesTarget = SamplesInAOI) %>%
  mutate(DiffScore = (SamplesTarget-SamplesDistractor)/(SamplesTarget+SamplesDistractor)) %>%
  mutate(ID = as.numeric(ID)) %>%
  mutate(experiment = ifelse((ID<17),1,ifelse((ID<33),2,(ifelse(ID<49,3,4))))) %>%
  mutate(ID = as.factor(ID))
```


```{r}
mresponse_time <- response_time %>%
  dplyr::select(experiment,ID,Target,trial,Time,DiffScore) %>%
  group_by(experiment,ID,Target,Time) %>%
  summarise(meandfind = mean(DiffScore, na.rm = TRUE)) %>%
  group_by(experiment,Target,Time) %>%
  #summarise(meandfexp = mean(meandfind, na.rm = TRUE))
  get_summary_stats(meandfind, type="mean_se") 

mresponse_time$experiment <- factor(mresponse_time$experiment,
                                    labels = c("Experiment 1", "Experiment 2", "Experiment 3", "Experiment 4"))

new_theme <- theme_light() +
  theme(strip.text = element_text(size = 14),
                panel.grid.major.y = element_line(colour="white"),
                panel.grid.major.x = element_line(colour="gray80", linetype = "longdash"),
                panel.grid.minor.y = element_blank(),        
                panel.grid.minor.x = element_blank(),
                legend.position="none",
                axis.text.y = element_text(size=12),
                axis.text.x = element_text(size=12),
                axis.title.y=element_text(size=16,face="bold"),
                axis.title.x = element_blank(),
                plot.title = element_text(size = 20))

theme_set(new_theme)

ptimecourse <- ggplot(data=mresponse_time, aes(x = Time, y = mean, color = Target)) +
  theme(
    strip.text.x = element_text(color = "black", size = 16, hjust = 0),
    strip.background = element_rect(fill = "white"),
    axis.title.x = element_text(size=16,face="bold"),
    legend.position = "bottom"
  ) +
  geom_vline(xintercept = 1500, linetype = "longdash", size = .35, color = "red") +
  geom_vline(xintercept = 3500, linetype = "longdash", size = .35, color = "red") +
  geom_hline(yintercept = 0, size = .35) +
  geom_line() +
  geom_ribbon(aes(ymin = mean - se, ymax = mean + se, fill = Target), alpha = 0.2, colour = NA) +
  scale_fill_manual(values = c("steelblue", "orange"),
                    name = "Condition", labels = c("Trained word", "Novel word")) +
  scale_color_manual(values = c("steelblue", "orange"),
                     name = "Condition", labels = c("Trained word", "Novel word")) +
  scale_y_continuous(name="Difference score", limits=c(-1.05, 1.05)) +
  scale_x_continuous(name="Time (ms)", limits=c(0, 5000), expand = c(0,0)) +
  facet_wrap(. ~ experiment, ncol = 1) 

ptimecourse
```


## Growth-curve analysis

```{r}
library(lme4)
```

```{r}
# sum-code and center our predictor:
response_time$TargetC <- ifelse(response_time$Target == 'Trained', .5, -.5)
response_time$TargetC <- as.numeric(scale(response_time$TargetC, center=TRUE, scale=FALSE))
```


```{r}
response_time_e1 <- response_time %>% filter(experiment == 1)
response_time_e2 <- response_time %>% filter(experiment == 2)
response_time_e3 <- response_time %>% filter(experiment == 3)
response_time_e4 <- response_time %>% filter(experiment == 4)
```

### Experiments

#### E1

```{r}
modelgca_e1 <- lmerTest::lmer(Elog ~ TargetC*(ot1 + ot2 + ot3 + ot4) + (1 + ot1 + ot2 + ot3 + ot4 | ID), 
                      data = response_time_e1,
                      control=lmerControl(optimizer="bobyqa"),
                      REML = FALSE)

broom.mixed::tidy(modelgca_e1, effects = "fixed") %>%
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

```{r}
plot(response_time, predictor_column = "Target", dv = "Elog", model = modelgca_e1) +
  theme_light()
```

```{r}
modelfits1 <- predictSE(modelgca_e1, response_time_e1)
modelfitse1 <- modelfits1 %>%
  bind_cols(response_time_e1) %>%
  mutate(se = se.fit) %>%
  mutate(ymin=fit-se, ymax=fit+se, inv_elog = exp(Elog)/(1+exp(Elog))) %>%
  mutate(experiment = 1)
```

#### E2

```{r}
modelgca_e2 <- lmerTest::lmer(Elog ~ TargetC*(ot1 + ot2 + ot3 + ot4) + (1 + ot1 + ot2 + ot3 + ot4 | ID), 
                      data = response_time_e2,
                      control=lmerControl(optimizer="bobyqa"),
                      REML = FALSE)

broom::tidy(modelgca_e2, effects = "fixed") %>%
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

```{r}
plot(response_time_e2, predictor_column = "Target", dv = "Elog", model = modelgca_e2) +
  theme_light()
```
```{r}
modelfits2 <- predictSE(modelgca_e2, response_time_e2)
modelfitse2 <- modelfits2 %>%
  bind_cols(response_time_e2) %>%
  mutate(se = se.fit) %>%
  mutate(ymin=fit-se, ymax=fit+se, inv_elog = exp(Elog)/(1+exp(Elog))) %>%
  mutate(experiment = 2)
```


#### E3

```{r}
modelgca_e3 <- lmerTest::lmer(Elog ~ TargetC*(ot1 + ot2 + ot3 + ot4) + (1 + ot1 + ot2 + ot3 + ot4 | ID), 
                      data = response_time_e3,
                      control=lmerControl(optimizer="bobyqa"),
                      REML = FALSE)

broom::tidy(modelgca_e3, effects = "fixed") %>%
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

```{r}
plot(response_time_e3, predictor_column = "Target", dv = "Elog", model = modelgca_e3) +
  theme_light()
```

```{r}
modelfits3 <- predictSE(modelgca_e3, response_time_e3)
modelfitse3 <- modelfits3 %>%
  bind_cols(response_time_e3) %>%
  mutate(se = se.fit) %>%
  mutate(ymin=fit-se, ymax=fit+se, inv_elog = exp(Elog)/(1+exp(Elog))) %>%
  mutate(experiment = 3)
```

#### E4

```{r}
modelgca_e4 <- lmerTest::lmer(Elog ~ TargetC*(ot1 + ot2 + ot3 + ot4) + (1 + ot1 + ot2 + ot3 + ot4 | ID), 
                      data = response_time_e4,
                      control=lmerControl(optimizer="bobyqa"),
                      REML = FALSE)

# cleanly show important parts of model (see `summary()` for more)
broom::tidy(modelgca_e4, effects = "fixed") %>%
  kable(digits = 3) %>% 
  kable_styling(bootstrap_options = "striped",
                full_width = F)
```

```{r}
plot(response_time_e4, predictor_column = "Target", dv = "Elog", model = modelgca_e4) +
  theme_light()
```

```{r}
modelfits4 <- predictSE(modelgca_e4, response_time_e4)
modelfitse4 <- modelfits4 %>%
  bind_cols(response_time_e4) %>%
  mutate(se = se.fit) %>%
  mutate(ymin=fit-se, ymax=fit+se, inv_elog = exp(Elog)/(1+exp(Elog))) %>%
  mutate(experiment = 4)
```

### GCA plots

```{r}
modelfits <- rbind(modelfitse1,modelfitse2,modelfitse3,modelfitse4) 

modelfits <- modelfits %>%
  mutate(experiment = as.factor(experiment)) %>%
  mutate(experiment = recode(experiment, `1` = "Experiment 1", `2` = "Experiment 2", 
                             `3` = "Experiment 3", `4` = "Experiment 4"))
```

```{r}
pgca <- ggplot(modelfits, aes(x=Time, y=fit, shape=Target, fill=Target, color=Target)) +
  theme(
    strip.text.x = element_text(color = "black", size = 16, hjust = 0),
    strip.background = element_rect(fill = "white"),
    axis.title.x = element_text(size=16,face="bold"),
    legend.position = "bottom"
  ) +
  geom_ribbon(aes(ymin=ymin, ymax=ymax),alpha=.2, color=NA)+
  geom_line() +
  geom_hline(yintercept = 0, size = .35) +
  stat_summary(data=modelfits,
               aes(x=Time, y=Elog), fun.y=mean, geom="point",
               alpha=0.6, size=.75) +
  geom_vline(xintercept = 1500, linetype = "longdash", size = .35, color = "red") +
  geom_vline(xintercept = 3500, linetype = "longdash", size = .35, color = "red") +
  scale_fill_manual(values = c("steelblue4", "orange4")) +
  scale_color_manual(values = c("steelblue4", "orange4")) +
  scale_y_continuous(name="E-log transformed \nproportion of target looking") + #, limits=c(-1.05, 1.05)) +
  scale_x_continuous(name="Time (ms)", limits=c(0, 5000), expand = c(0,0)) +
  facet_wrap(. ~ experiment, ncol = 1)
  facet_wrap(. ~ experiment, ncol = 1)
  
pgca
```

## Figure 3
```{r}
ggarrange(ptimecourse, NULL, pgca, widths = c(1,.05,.75),
          ncol = 3,
          labels = c("A"," ", "B"),
          common.legend = T, legend = "bottom")

ggsave("plots/figure_timecourse.png", plot = last_plot(), width = 30, height = 20, units = c("cm"))
```

## Cluster-based permutation analysis

```{r}
library(pbapply)
```

```{r}
# aggregate across trials within subjects in time analysis
aux_d_byID <- make_time_sequence_data(response_window, time_bin_size = sizebin, 
                                 predictor_columns = c("Target"),
                                 aois = c("DistractorObj"),
                                 summarize_by = "ID"
                            )

response_time_byID <- make_time_sequence_data(response_window, time_bin_size = sizebin, 
                                 predictor_columns = c("Target"),
                                 aois = "ActedObj",
                                 summarize_by = "ID"
                            ) %>%
  mutate(SamplesDistractor = aux_d_byID$SamplesInAOI) %>%
  mutate(SamplesTarget = SamplesInAOI) %>%
  mutate(DiffScore = (SamplesTarget-SamplesDistractor)/(SamplesTarget+SamplesDistractor)) %>%
  mutate(DiffScoreConstant = ifelse(SamplesTotal > 0, 0,NaN)) %>%
  mutate(ID = as.numeric(ID)) %>%
  mutate(experiment = ifelse((ID<17),1,ifelse((ID<33),2,(ifelse(ID<49,3,4))))) %>%
  mutate(ID = as.factor(ID))
```

```{r}
rtIDe1 <- response_time_byID %>% filter(experiment == 1)
rtIDe2 <- response_time_byID %>% filter(experiment == 2)
rtIDe3 <- response_time_byID %>% filter(experiment == 3)
rtIDe4 <- response_time_byID %>% filter(experiment == 4)
```


```{r}
num_sub = 16 #length(unique((response_time_e1$ID)))
threshold_t = qt(p = 1 - .05/2, 
                 df = num_sub-1) # pick threshold t based on alpha = .05 two tailed
```

#### E1 

```{r}
df_timeclust <- make_time_cluster_data(rtIDe1, 
                                      test= "t.test", paired=TRUE,
                                      predictor_column = "Target", 
                                      threshold = 2,
                                      formula = DiffScore ~ Target)

plot(df_timeclust) + ylab("T-Statistic") + theme_light()

summary(df_timeclust)

clust_analysis <- analyze_time_clusters(df_timeclust, within_subj=TRUE, paired=TRUE,
                                        samples=1000)

plot(clust_analysis) + theme_light()
summary(clust_analysis)
```
#### E2

```{r}
df_timeclust <- make_time_cluster_data(rtIDe2, 
                                      test= "t.test", paired=TRUE,
                                      predictor_column = "Target", 
                                      threshold = 2,
                                      formula = DiffScore ~ Target) 

plot(df_timeclust) + ylab("T-Statistic") + theme_light()

summary(df_timeclust)

clust_analysis <- analyze_time_clusters(df_timeclust, within_subj=TRUE, paired=TRUE,
                                        samples=1000)

plot(clust_analysis) + theme_light()
summary(clust_analysis)
```

#### E3

```{r}
df_timeclust <- make_time_cluster_data(rtIDe3, 
                                      test= "t.test", paired=TRUE,
                                      predictor_column = "Target", 
                                      threshold = 2,
                                      formula = DiffScore ~ Target) 
plot(df_timeclust) + ylab("T-Statistic") + theme_light()

summary(df_timeclust)

clust_analysis <- analyze_time_clusters(df_timeclust, within_subj=TRUE, paired=TRUE,
                                        samples=1000) # in practice, you should use a lot more

plot(clust_analysis) + theme_light()
summary(clust_analysis)
```

#### E4

```{r}
df_timeclust <- make_time_cluster_data(rtIDe4, 
                                      test= "t.test", paired=TRUE,
                                      predictor_column = "Target", 
                                      threshold = 2,
                                      formula = DiffScore ~ Target) 
plot(df_timeclust) + ylab("T-Statistic") + theme_light()

summary(df_timeclust)

clust_analysis <- analyze_time_clusters(df_timeclust, within_subj=TRUE, paired=TRUE,
                                        samples=1000) # in practice, you should use a lot more

plot(clust_analysis) + theme_light()
summary(clust_analysis)
```

## Test onset analysis

This analysis summarizes where infants looked at the begining of the test measurement period and how rapidly they sacccaded to one of the objects.

```{r}
library(data.table)

resultsvisits<-resultsclean %>%
  group_by(experiment,ID,trial) %>%
  mutate(visitID = rleid(AOI)) %>%
  group_by(experiment,ID,trial,visitID) %>% 
        mutate(frameStart = min(sample),
               frameEnd = max(sample)) %>%
                    filter(sample == min(sample)) %>%
                mutate(visitDuration = frameEnd - frameStart+1,
                       visitms = visitDuration*1000/60) %>%
                    select(ID, trial, trialtype, timebin, visitID, AOI, visitDuration, visitms, frameStart, frameEnd, timems)

#Compute the number of contributed trials
contributedtrials <- resultsclean %>%
  group_by(experiment,ID) %>%
  summarise(ctrials = n_distinct(trial))

##

resultsfirstlooks <- resultsvisits %>%
  filter(AOI == "target" | AOI == "distractor") %>%
  group_by(experiment,ID,trial,trialtype) %>%
  mutate(visitObjectID = rleid(visitID)) %>%
  filter(visitObjectID == 1) %>%
  mutate(latency = frameStart*1000/60) %>%
  group_by(experiment,ID,trialtype) %>%
  summarise(target = sum(AOI %in% c("target")), 
            distractor = sum(AOI %in% c("distractor")),
            ptarget = target/(target+distractor),
            mlatency = mean(latency)) 

resultsfirstlooks %>%
  group_by(experiment, trialtype) %>%
  summarise(ptargetgav = mean(ptarget),
            latencygav = mean(mlatency))

resultsfirstlooks %>%
  group_by(experiment) %>%
  summarise(ptargetgav = mean(ptarget),
            latencygav = mean(mlatency)) 

resultsvisits <- merge(resultsvisits,contributedtrials,by = c("experiment","ID"))

resultsvisits %>%
  filter(AOI == "center") %>%
  group_by(experiment,trialtype) %>%
  summarise(mean(visitms), min(visitms), max(visitms))

resultsvisits %>%
  filter(AOI == "center") %>%
  group_by(experiment,trialtype) %>%
  ggplot(aes(x = as.factor(experiment), y = visitms, color = as.factor(experiment), fill=experiment)) +
  theme_light() +
  geom_boxplot() +
  #geom_jitter(size = .5) +
  stat_summary(fun.data = mean_se, color = "black",shape=18, size = 1, position=position_dodge(.75)) +
  ggtitle("Duration of central fixation at the trial onset") +
  facet_grid(. ~ trialtype)
  
auxbis <- resultsvisits %>%
  group_by(experiment,ID,trial) %>%
  filter(visitID %in% c(1)) %>%
  arrange(ID) %>%
  group_by(experiment,ID,AOI,ctrials) %>%
  summarise(a = n()) %>%
  pivot_wider(names_from = "AOI", values_from = c("a"), values_fn = unique) 

names(auxbis)[5] <- "nodata"

auxbis[is.na(auxbis)] <- 0

auxbis %>%
  mutate(pcenter = ifelse(is.na(center),0,center/ctrials),
         ptarget = ifelse(is.na(target),0,target/ctrials),
         pdistractor = ifelse(is.na(distractor),0,distractor/ctrials),
         pelse = ifelse(is.na(TrackLoss),0,TrackLoss/ctrials),
         pnodata = ifelse(is.na(nodata),0,nodata/ctrials)) %>%
  gather(key = "AOI", value=trialproportion, c("pcenter", "ptarget", "pdistractor", "pelse", "pnodata")) %>%
  group_by(experiment,AOI) %>% 
  summarise(trialproportion = mean(trialproportion)) 

auxbis %>%
  mutate(pcenter = ifelse(is.na(center),0,center/ctrials),
         ptarget = ifelse(is.na(target),0,target/ctrials),
         pdistractor = ifelse(is.na(distractor),0,distractor/ctrials),
         pelse = ifelse(is.na(TrackLoss),0,TrackLoss/ctrials),
         pnodata = ifelse(is.na(nodata),0,nodata/ctrials)) %>%
  gather(key = "AOI", value=trialproportion, c("pcenter", "ptarget", "pdistractor", "pelse", "pnodata")) %>%
  mutate(AOI = as.factor(AOI)) %>%
  mutate(AOI = recode(AOI, `pcenter` = "Center (attention getter)", `ptarget` = "Target", 
                             `pdistractor` = "Distractor", `pelse` = "Else", `pnodata` = "No data available")) %>%
  group_by(experiment,AOI) %>%
  ggplot(aes(x = as.factor(experiment), y = trialproportion, color = AOI, fill = AOI)) +
  theme_light() +
  geom_boxplot(alpha = .2) +
  stat_summary(fun.data = mean_se, color = "black",shape=18, size = .55, position=position_dodge(.75)) +
  scale_y_continuous(name="Proportion of valid trials") + #, limits=c(-1.05, 1.05)) +
  xlab("Experiment") +#, limits=c(0, 5000), expand = c(0,0)) +
  ggtitle("Location of gaze at the onset of the test measurement period") 

ggsave("plots/figure_s2.png", plot = last_plot(), width = 20, height = 10, units = c("cm"))
```


